Supplementary material: Disease Knowledge Transfer across Neurodegenerative Diseases

### 2019-07-16 paper/supplementary.tex
submitted camera-ready versiong

% * <mrazvan22@gmail.com> 2018-03-02T16:41:47.321Z:
% 
% Author list: Me, Marco (writing+model code), Stefano, Alex Young (writing+tadpole), Pere (helped with validation),Neil (tadpole),  Arman, Keir (DTI data), Seb, Danny
% 
% ^ <mrazvan22@gmail.com> 2018-03-02T16:55:06.003Z.

% \author{******************}

\author{}

@@

\institute{}

% \institute{Centre for Medical Image Computing, University College London, UK
% \and 
% Queen Square MS Centre, UCL Institute of Neurology, UK
% \and 
% Dementia Research Centre, University College London, UK
% \and
% University of C\^{o}te d'Azur, Inria Sophia Antipolis, France
% % Laboratoire d'Analyse Num\'{e}rique, B\^{a}timent 425,\\
% % F-91405 Orsay Cedex, France}
% }

@@

We generated the synthetic data as follows, using parameters from Table \ref{tab:synParams}:
\begin{itemize}
 \item We simulate two synthetic diseases, "synthetic PCA" and "synthetic AD"
 \item We define 6 biomarkers that we allocate to agnostic units $l_0$ and $l_1$ (Table \ref{tab:synParams} top)
 \item Within each agnostic unit, we define the parameters $theta_0$ -- $theta_5$ corresponding to biomarker trajectories within the agnostic unit.
 \item For each disease, we define the parameters $\lambda$ corresponding to trajectories of dysfunction scores.
 \item We then sample data from 100 synthetic AD subjects and 50 PCA subjects with $\beta_i$ as given in Table \ref{tab:synParams} bottom using the model likelihood (Eq. 2 from main paper). For each subject, we generate data for 4 visits, each 1 year apart.
\end{itemize}

@@

The cohort from the Dementia Research Center UK used for validation had the following demongraphics: 10 subjects diagnosed with Posterior Cortical Atrophy, with a mean age of 59.4, 40\% females, as well as 10 age-matched controls with a mean age of 59.3, 50\% females.

For the validation on TADPOLE subtypes, we used applied the SuStaIn model on TADPOLE to split the population into three subtypes with different progression: a hippocampal subtype \TODODODO
When splitting the TADPOLE subjects into three populations with different progressions, the resulting groups had the following demographics:

\begin{table}
 \begin{tabular}{c | c c c c}
\textbf{Cohort} & \textbf{Nr. subjects} & \textbf{Nr. visits} & \textbf{Age (baseline)} & \textbf{Gender (\%F)}\\
\hline
Controls (Hippocampal) & 31 & 2.3 $\pm$ 1.8 & 74.4 $\pm$ 6.9 & 38\%\\
AD (Hippocampal) & 21 & 1.5 $\pm$ 0.8 & 74.5 $\pm$ 5.5 & 42\%\\
\hline
Controls (cortical) & 21 & 2.3 $\pm$ 1.3 & 70.9 $\pm$ 5.4 & 42\%\\
AD (cortical) & 35 & 1.7 $\pm$ 0.9 & 72.8 $\pm$ 7.4 & 28\%\\
\hline
Controls (subcortical) & 28 & 3.0 $\pm$ 1.5 & 73.7 $\pm$ 6.5 & 42\%\\
AD (subcortical) & 27 & 1.6 $\pm$ 0.9 & 73.7 $\pm$ 7.5 & 33\%\\
 \end{tabular}
 \caption{Demo}
 \label{tab:demogTadSubtypes}
\end{table}

% \begin{table}
%  \begin{tabular}{c | c c c}
%   Cohort & Number of scans & Age & Gender (\%F)\\
%   Controls & 10 & 59.4 & 50\%\\
%   PCA & 10 & 59.3 & 40\%\\
%  \end{tabular}
% \end{table}

\bibliographystyle{unsrtnat}
\begin{thebibliography}{5}

\end{thebibliography}

\clearpage

>>>>

\author{R\u{a}zvan V. Marinescu\inst{1,2} \and Marco Lorenzi\inst{5} \and Stefano Blumberg\inst{1} \and Alexandra L. Young\inst{1} \and Pere Planell-Morell\inst{1} \and Neil P. Oxtoby\inst{1} \and Arman Eshaghi\inst{1,3} \and Keir X. Young\inst{4} \and Sebastian J. Crutch\inst{4} \and Polina Golland\inst{2} \and Daniel C. Alexander\inst{1}, for the Alzheimer's Disease Neuroimaging Initiative}

@@

% \institute{}

\institute{Centre for Medical Image Computing, University College London, UK
\and 
Computer Science and Artificial Intelligence Laboratory, MIT, USA
\email{razvan@csail.mit.edu}
\and
Queen Square MS Centre, UCL Institute of Neurology, UK
\and 
Dementia Research Centre, University College London, UK
\and
University of C\^{o}te d'Azur, Inria Sophia Antipolis, France
% Laboratoire d'Analyse Num\'{e}rique, B\^{a}timent 425,\\
% F-91405 Orsay Cedex, France}
}

@@

We generated the synthetic data as follows, using parameters from Table \ref{tab:synParams}:
\begin{itemize}
 \item We simulate two synthetic diseases, "synthetic PCA" and "synthetic AD"
 \item We define 6 biomarkers that we allocate to agnostic units $l_0$ and $l_1$ (Table \ref{tab:synParams} top)
 \item Within each agnostic unit, we define the parameters $\{\theta_0$, ..., $\theta_5\}$ corresponding to biomarker trajectories within the agnostic unit.
 \item For each disease, we define the parameters $\lambda$ corresponding to trajectories of dysfunction scores.
 \item We then sample data from 100 synthetic AD subjects and 50 PCA subjects with $\beta_i$ as given in Table \ref{tab:synParams} bottom using the model likelihood (Eq. 2 from main paper). For each subject, we generate data for 4 visits, each 1 year apart.
\end{itemize}

@@

The cohort from the Dementia Research Centre UK used for validation consisted of 10 subjects diagnosed with Posterior Cortical Atrophy, with a mean age of 59.4, 40\% females, as well as 10 age-matched controls with a mean age of 59.3, 50\% females.

For the validation on TADPOLE subgroups, we used applied the SuStaIn model on TADPOLE to split the population into three subgroups with different progression: hippocampal, cortical and subcortical subypes with prominent atrophy in the hippocampus, cortical and subcortical areas respectively.
The resulting subgroups had the following demographics:

\begin{table}
 \begin{tabular}{c | c c c c}
\textbf{Cohort} & \textbf{Nr. subjects} & \textbf{Nr. visits} & \textbf{Age (baseline)} & \textbf{Gender (\%F)}\\
\hline
Controls (Hippocampal) & 31 & 2.3 $\pm$ 1.8 & 74.4 $\pm$ 6.9 & 38\%\\
AD (Hippocampal) & 21 & 1.5 $\pm$ 0.8 & 74.5 $\pm$ 5.5 & 42\%\\
\hline
Controls (cortical) & 21 & 2.3 $\pm$ 1.3 & 70.9 $\pm$ 5.4 & 42\%\\
AD (cortical) & 35 & 1.7 $\pm$ 0.9 & 72.8 $\pm$ 7.4 & 28\%\\
\hline
Controls (subcortical) & 28 & 3.0 $\pm$ 1.5 & 73.7 $\pm$ 6.5 & 42\%\\
AD (subcortical) & 27 & 1.6 $\pm$ 0.9 & 73.7 $\pm$ 7.5 & 33\%\\
 \end{tabular}
 \caption{Demographics of the subjects in the three TADPOLE subgroups.}
 \label{tab:demogTadSubtypes}
\end{table}

% \bibliographystyle{unsrtnat}
% \begin{thebibliography}{5}
% 
% \end{thebibliography}
% 
% \clearpage
